#Markdown Notes

```{r, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(knitr)
library(lme4)
library(lmerTest)
library(gridExtra)
library(corrplot)
library(GGally)
library(kableExtra)
```

```{r}
load("36806-0001-Data.rda")
ChicagoForeignCouncilRaw<-as.data.frame(da36806.0001)
#This will just allow use to reform this data in a more helpful way, so that we don't need to worry about it. This is the 2016 Edition of this file

#Now We will need to clean the data. We will start off by removing the variables that are not useful to us. 

# I have observed the 2015 file of this data, in the Chicago Foreign Council. It phrases questions differently then the question that we have previously observed. Instead of looking at the same phrasing related to military intervention, it instead poses it as "Are you Pro or Anti Drone Strikes". This is a valuable question, no doubt, but it leaves our discussion open to survey bias. We cannot compare whether someone answers "How Effective do you think each of the following approaches are to achieving the foreign policy goals of the United States-Very Effective, somewhat,not very not at all" and "Drone Strikes against suspected terrorists in other countries". These evoke two different responses, and thus we cannot consider them equivalent. 


ChicagoForeignCouncilRaw2<-ChicagoForeignCouncilRaw %>%
  select(CASEID, XPHISPAN, DOV_Q8_14,PPAGE,PPEDUC,PPEDUCAT,PPETHM,PPGENDER,PPHHHEAD,PPHHSIZE,PPHOUSE,PPINCIMP,PPMARIT,PPMSACAT,PPREG4,PPREG9,PPRENT,PPSTATEN,PPWORK,PPNET,Q8_14,Q385,Q275)

ChicagoForeignCouncilRaw2<-ChicagoForeignCouncilRaw2[complete.cases(ChicagoForeignCouncilRaw2),]

#OTHER INTERESTING VARIABLES: ORLANDO, USR, MSC, CBSAMET

#Insert Here what data might be appropriate: 
# CASEID, XPHISPAN, ORLANDO, USR, MSC, CBSAMET, DOV_Q8_14,PPAGE,PPEDUC,PPETHM,PPGENDER,PPHHHEAD,PPHHSIZE,PPHOUSE,PPINCIMP,PPMARIT,PPMSACAT,PPREG4,PPREG9,PPRENT,PPSTATEN,PPWORK,PPNET,Q8_14,Q385,Q275

# I MIGHT CONSIDER Q278 and the associated questions important for figuring this shit out. 
summary(ChicagoForeignCouncilRaw2)
ChicagoForeignCouncilClean<-ChicagoForeignCouncilRaw2 %>%
  mutate(HISPANIC=ifelse(XPHISPAN=="(1) No, I am not",0,1),
         MALE=ifelse(PPGENDER=="(1) Male",1,0),
         IsHouseholdHead=ifelse(PPHHHEAD=="(0) NO",0,1),
         State=substring(PPSTATEN,5),
         Region4=substring(PPREG4,4),
         Region9=substring(PPREG9,4),
         StatementNumber=substring(DOV_Q8_14,2,2),
         InterventionSet1=substring(Q8_14,2,2)) %>%
    mutate(ProWarBinary=ifelse(InterventionSet1>2,0,1),
           ProWarFactor=as.factor(ProWarBinary)) %>%
    mutate(AgeBracket=ifelse(PPAGE<=24,"18-24",
                       ifelse(PPAGE<=34,"25-34",
                       ifelse(PPAGE<=44,"35-44",
                       ifelse(PPAGE<=64,"45-64","65+"))))) %>%
    mutate(EducationNumber=as.integer(substring(PPEDUC,2,3))) %>%
    mutate(EducationBracket=ifelse(EducationNumber<5,"1.Less Than Ninth Grade",
                             ifelse(EducationNumber<=8,"2.High School, No Diploma",
                             ifelse(EducationNumber==9,"3.High School Graduate",
                             ifelse(EducationNumber==10,"4.Some College, No Degree",
                             ifelse(EducationNumber==11,"5. Associate's Degree",
                             ifelse(EducationNumber==12, "6.Bachelor's Degree","7.Graduate Degree")))))),
           EducationBracket2=ifelse(EducationNumber<=8, "1. No High School Diploma",
                             ifelse(EducationNumber==9,"2. High School Graduate",
                              ifelse(EducationNumber==10,"3.Some College, No Degree",
                             ifelse(EducationNumber==11,"4. Associate's Degree",
                             ifelse(EducationNumber==12, "5.Bachelor's Degree","6.Graduate Degree")))))) %>%
  
  select(-XPHISPAN,-PPGENDER,-PPHHHEAD,-PPSTATEN,-PPREG4,-PPREG9,-EducationNumber,-PPAGE,)

#We have created two different education brackets. This will, in part, determine how many different variables might exist in order to determine the exact variable. 

summary(factor(ChicagoForeignCouncilClean$StatementNumber))

summary(factor(ChicagoForeignCouncilClean$PPINCIMP))

summary(factor(ChicagoForeignCouncilClean$PPEDUC))

summary(factor(ChicagoForeignCouncilClean$AgeBracket))

summary(factor(ChicagoForeignCouncilClean$EducationBracket2))

summary(factor(ChicagoForeignCouncilClean$State))

summary(factor(ChicagoForeignCouncilClean$Region9))

# I made preference towards intervention a binary variable. I chose to make Very Effective and Somewhat Effective variables that might suggest these people would be "open" to war. However, those who answer Not very, or Not effective at all are extremely unlikely to support war. 

# I should also consider how I might want to adjust the variable that shows household income. There is a chance that it is over-strata-d. This would be a problem. 
```

```{r}
ggplot(ChicagoForeignCouncilClean,aes(x=StatementNumber,fill=InterventionSet1))+geom_bar(position=position_fill())
#This is a graph meant to see if the order that the statement is shown in might be important to determining the preferences or the stated ideals that an individual has
```
By observing this data, we can see that there is no apparent distinction that exists between opinions of war, and whether or not this determine the factors that might lead to war.

```{r}
ggplot(ChicagoForeignCouncilClean,aes(x=Region4,fill=InterventionSet1))+geom_bar(position=position_fill())
#This plot will attempt to analyze whether there is a preference for war by region, such as region 4, or region 9, or state perhaps even. We can see that there does appear to be some slight preference, particularly in the south and in the Midwest. 
ggplot(ChicagoForeignCouncilClean,aes(x=Region9,fill=InterventionSet1))+geom_bar(position=position_fill())+theme(axis.text.x=element_text(angle=90))

```
```{r}
#ggplot(ChicagoForeignCouncilClean,aes(x=StatementNumber,fill=InterventionSet1))+geom_bar(position=position_fill())
ggplot(ChicagoForeignCouncilClean,aes(x=AgeBracket,fill=ProWarFactor))+geom_bar(position=position_fill())
```
```{r}
ggplot(ChicagoForeignCouncilClean,aes(x=EducationBracket2,fill=ProWarFactor))+geom_bar(position=position_fill())+theme(axis.text.x=element_text(angle=90))

# We are able to see here that, as education goes up, we are able to continue to have more and more variables. 
```

```{r}
ggplot(ChicagoForeignCouncilClean,aes(x=PPETHM,fill=ProWarFactor))+geom_bar(position=position_fill())+theme(axis.text.x=element_text(angle=90))
# Cite this as a point of the limitations with MRP. For instance, there are significant problems in our data, and MRP. It forces us to better understand why exactly this is happening. We could, potentially, do some analysis about other variables. However, in general, this is a problem with MRP, and needing to use the ACS
```
```{r}
ggplot(ChicagoForeignCouncilClean,aes(x=PPHHSIZE,fill=ProWarFactor))+geom_bar(position=position_fill())
# This indicates there might be some kind of relationship between HHSIZE and Pro vs. Anti War sentiment. However, it might also be caused by a low sample size for some of the smaller variables. 
```
```{r}
summary(as.factor(ChicagoForeignCouncilClean$PPHHSIZE))
#This can be verified here. There are only 55 households with six people. This is probably not a sufficient sample size. 
```
```{r}
ggplot(ChicagoForeignCouncilClean,aes(x=PPHOUSE,fill=ProWarFactor))+geom_bar(position=position_fill())+theme(axis.text.x=element_text(angle=90))
# Based on this variable, there is not a severe relationship between housing in general. However, people that live in mobile homes appear to be substantially more likely to be pro war. I feel like this might be partially explained by other variables
```
```{r}
ggplot(ChicagoForeignCouncilClean,aes(x=PPINCIMP,fill=ProWarFactor))+geom_bar(position=position_fill())+theme(axis.text.x=element_text(angle=90))
# Here, it appears that as individuals get more walthy, there is a little bit of lower pro war sentiment. 
```
```{r}
ggplot(ChicagoForeignCouncilClean,aes(x=PPMARIT,fill=ProWarFactor))+geom_bar(position=position_fill())+theme(axis.text.x=element_text(angle=90))
# Marital STatus does not appear to be a determining factor in pro v. anti war sentiment. In particular, we might be concerned about the variable Living with Partner. However, this variable has a rather low count for the total number of occurances. Therefore, I am not very concerned about it. 
```

```{r}
ggplot(ChicagoForeignCouncilClean,aes(x=PPNET,fill=ProWarFactor))+geom_bar(position=position_fill())+theme(axis.text.x=element_text(angle=90))
#People without internet tend to be more likely to be prowar. However, 
```
```{r}
ggplot(ChicagoForeignCouncilClean,aes(x=PPMSACAT,fill=ProWarFactor))+geom_bar(position=position_fill())+theme(axis.text.x=element_text(angle=90))
#People both in and outside of cities appear to have equal perceptions on the success of military intervention. 
```
```{r}
ggplot(ChicagoForeignCouncilClean,aes(x=PPRENT,fill=ProWarFactor))+geom_bar(position=position_fill())

#+theme(axis.text.x=element_text(angle=90))
#Housing Situation appears to have very little influence on the perception of War
```

```{r}
#Introductory Models
#M0<-glmer(data=ChicagoForeignCouncilClean,ProWarBinary~1+(1|State),family=binomial(link="logit"))
#summary(M0)
#M1<-glmer(data=ChicagoForeignCouncilClean,ProWarBinary~MALE+HISPANIC+(1|State),family=binomial(link="logit"))
#summary(M1)
#M2<-glmer(data = ChicagoForeignCouncilClean,ProWarBinary~MALE+HISPANIC+PPAGE+(1|State),family=binomial(link="logit"))
#summary(M2)
#M3<-glmer(data= ChicagoForeignCouncilClean,ProWarBinary~factor(PPEDUCAT)+(1|State),family=binomial(link="logit"))
#summary(M3)
#After working with all of these variables, one remarkably thing that I have seen is that it appears like relatively limited amount of this is determined by things such as education or gender. 
#M4<-glmer(data= ChicagoForeignCouncilClean,ProWarBinary~factor(PPEDUCAT)+MALE+(1|State),family=binomial(link="logit"))
#summary(M4)
#M5<-glmer(data= ChicagoForeignCouncilClean,ProWarBinary~factor(PPEDUCAT)+MALE+(1|Region9),family=binomial(link="logit"))
#summary(M5)

#M6<-glmer(data= ChicagoForeignCouncilClean,ProWarBinary~factor(PPEDUCAT)+MALE+factor(PPETHM)+(1|State),family=binomial(link="logit"))
#summary(M6)

#M7<-glmer(data= ChicagoForeignCouncilClean,ProWarBinary~factor(PPEDUCAT)+MALE+factor(PPETHM)+factor(PPINCIMP)+(1|State),family=binomial(link="logit"))
#summary(M7)

#M7<-glmer(data= ChicagoForeignCouncilClean,ProWarBinary~factor(PPEDUCAT)+factor(PPETHM)+factor(PPINCIMP)+(1|State),family=binomial(link="logit"))
#summary(M7)

#M8<-glmer(data= ChicagoForeignCouncilClean,ProWarBinary~MALE+factor(PPEDUCAT)+factor(AgeBracket)+(1|State),family=binomial(link="logit"))
#summary(M8)

#M9<-glmer(data= ChicagoForeignCouncilClean,ProWarBinary~factor(AgeBracket)+factor(PPETHM)+factor(PPINCIMP)+(1|State),family=binomial(link="logit"))
#summary(M9)

#M10<-glmer(data= ChicagoForeignCouncilClean,ProWarBinary~MALE*factor(AgeBracket)+factor(PPEDUCAT)+(1|State),family=binomial(link="logit"))
#summary(M10)

#M11<-glmer(data= ChicagoForeignCouncilClean,ProWarBinary~MALE*factor(PPEDUCAT)+factor(AgeBracket)+(1|State),family=binomial(link="logit"))
#summary(M11)

#M12<-glmer(data= ChicagoForeignCouncilClean,ProWarBinary~Region9*MALE+factor(PPEDUCAT)+factor(AgeBracket)+(1|State),family=binomial(link="logit"))
#summary(M12)

#M13<-glm(data=ChicagoForeignCouncilClean,ProWarBinary~State,family=binomial(link="logit"))
#summary(M13)

#M14<-glmer(data= ChicagoForeignCouncilClean,ProWarBinary~MALE+factor(PPEDUCAT)+factor(AgeBracket)*Region4+(1|State),family=binomial(link="logit"))
#summary(M14)

#M15<-glmer(data= ChicagoForeignCouncilClean,ProWarBinary~MALE+factor(EducationBracket)+factor(AgeBracket)+(1|State),family=binomial(link="logit"))
#summary(M15)

M16<-glmer(data= ChicagoForeignCouncilClean,ProWarBinary~MALE+factor(EducationBracket2)+factor(AgeBracket)+(1|State),family=binomial(link="logit"))
summary(M16)

#State does perform better that Region in these tests. However, the number of responses per state is very low. Therefore, there may be more benefit in using something like region9. This will be, in hindsight, what I choose to use moving forward


#M17<-glmer(data= ChicagoForeignCouncilClean,ProWarBinary~MALE+factor(EducationBracket2)+factor(AgeBracket)+(1|Region9),family=binomial(link="logit"))
#summary(M17)

#Up to this point, I've found that Education Level, broken into Strata, and Age Brackets seems to be a good predictor. I've elected to choose to move forward with a model if it is supported by the ACS. In addition, I have decided to move forward with a model if it is able to break the population into sufficiently small stratas.

M18<-glmer(data= ChicagoForeignCouncilClean,ProWarBinary~MALE+factor(EducationBracket2)+factor(AgeBracket)+(1|State),family=binomial(link="logit"))
summary(M18)
```
I feel like Model 16 works the best of anything that I have seen so far. Therefore, we are able to find a lot of different variables, and what their expected values are. In addition, we can observe some of the effects in r of each random effect. 

```{r}
FullCoefficientsList<-coef(M16)$State
FullCoefficientsList
StateRandomEffects<-FullCoefficientsList[,0:1]
#This Will allow us to understand what variable is the most important for this

# Background says that Men tend to be more pro-war, 
# Background says that higher levels of education tend to 
# 
```

```{r}
#One important thing to notice is the intercepts don't change. Therefore, we should be able to define each of these variables. Unfortunately, there are a lot of Different Variables

CMale<-M16@beta[2]
CHSGrad<-M16@beta[3]
CSomeCollege<-M16@beta[4]
CAssociates<-M16@beta[5]
CBachelor<-M16@beta[6]
CGraduate<-M16@beta[7]
C25_34<-M16@beta[8]
C35_44<-M16@beta[9]
C45_64<-M16@beta[10]
C65Plus<-M16@beta[11]


#We have now broken our variables into roughly 60 Stratas. We have 2 variables to indicate gender identity, there are 6 Education Brackets, and there are 5 Age Brackets. 


```

```{r}
library(rstanarm)

fit<-stan_glmer(data=ChicagoForeignCouncilClean,ProWarBinary~MALE+factor(EducationBracket2)+factor(AgeBracket)+(1|State),family=binomial(link="logit"))
```
```{r}
summary(fit)
```






