This is simply a new R file that I am using. We will see if this might come into play later. It may be where I create the final step of my project. 

We have now reached a point where we can move forward. I feel like Model 25 has been the best model that we have found recently. This will mean that we can move forward. We have also created State by State model estimates. That is all pretty cool

```{r}
KeyVariables<-colnames(estimates)

CellPerc2<-as.data.frame(CellPerc) %>% dplyr::select(KeyVariables) %>%
  arrange(STUSPS)

estimates2 <- estimates %>% arrange(STUSPS)

Weights<-CellPerc2[,2:51]
ProbabilityPro<-estimates2[,2:51]
row.names(ProbabilityPro)<-CellPerc2$STUSPS



EstimatedProbability<-rep(NA,51)

df<-data.frame(RawEstimates,EstimatedProbability)


metadataStateGIS<-data.frame(metadataStateGIS,EstimatedProbability)

metadataStateGIS <-metadataStateGIS %>% arrange(STUSPS)

df <- df %>% arrange(State)
                     

#Use a for loop in order to get these solutions

#MAP, vs. #Heat MAP
```

```{r}
for (i in 1:51) {
  df[i,4]<-(sum(Weights[i,]*ProbabilityPro[i,])*100)
}
```

```{r}
for (i in 1:51) {
  metadataStateGIS[i,75]<-(sum(Weights[i,]*ProbabilityPro[i,])*100)
}
```


```{r}
df<-df %>%
  mutate(SSR=(EstimatedProbability-PercentSupportSampled)^2)

df2<-df[2:51,]

# First 
```

```{r}
# Define SSR

ggplot(data=df2,aes(x=Number.Sampled,y=SSR,label=State))+geom_point()+geom_text(nudge_y=.4)

# Change wording to Sample Size

# What we see here is what we expect: As sample gets larger, we get a better estimate of the population level of support. 

# Look more into create observations
```


```{r}

```




