Based on the Book "Paying the Human costs of War, we are introduced to some interesting topics about how support for War may work. Therefore, we might decide to bring some priors into this discussion. For instance, There is the likelihood to be a "Timid Hawk". A Timid Hawk, according to the book, refers to individuals who tend to be pro conflict, or pro intervention, but tend to not want to pay the human costs of war. This fits into a fascinating paradigm that we can think of war as. 

```{r}
library(rstanarm)
library(bayesplot)
```

```{r}
#PriorMeans<-c(,rep(0,51))
# this would be good for us to find our new definitions
#myprior<-normal(location=c())

ProWar_Model_Prior<-stan_glmer(data=ChicagoForeignCouncilClean,ProWarBinary~MALE+EducationBracket3+AgeBracket+(1|State),
              family=binomial(link="logit"),
              prior_intercept = normal(.5,2),
              prior = normal(0,2, autoscale = TRUE),
              chains=4,iter=5000,seed=050822,
              prior_PD = TRUE)
              
# for a weakly informative, we might want to use a different variance. Use a larger variance for a weakly informative model. 

# lower the number of chains, and increase the number of iterations. 

# read a little bit of the Bayesian Data Analysis book. Read Chapter 11, section 11.4

# Say a little bit about how you have tried to assess convergence

# check the convergence out a little bit

# Specify the number of iterations and chains, in order to ensure that it is working properly. 

#Check out the Gelman Rubin and the Geweke

#Make sure that the chains converge and that they are mixing well. 

# Before next meeting: Look at Gelman Rubin and Geweke, see which works better on the Analysis we are doing. , Continue to work on Priors, I should wind up with a series of different trace plots. 

# We use the prior intercept, and estimate that it is based around 60%, based on prior research on pro vs. anti war sentiment. This would match with, approximately, a .6 
```
```{r}
ProWar_Model_Prior
```


```{r}
prior_summary(ProWar_Model_Prior)
summary(ProWar_Model_Prior,effects="fixed",conf.int=TRUE)
```

```{r}
ProWar_Model_Posterior<-update(ProWar_Model_Prior,prior_PD=FALSE)
```


```{r}
print(ProWar_Model_Posterior)
summary(ProWar_Model_Posterior)

#THIS BAYESIAN COMPONENT IS A FUCKING NIGHTMARE, with how all of this is set up. 


```
```{r}
ChicagoForeignCouncilBayes<-ChicagoForeignCouncilClean %>%
  dplyr::select(CASEID,ProWarBinary,MALE,EducationBracket3,AgeBracket,State) %>%
  mutate()
```


```{r}
# This is copied from MRP in rstanarm. This is important in order to do our MRP Function

# A significant problem here is the differences in formatting. Because of this, I will either have to switch the Original Chicago Foreign Council File, or the new file


Stratas<-colnames(estimates)[2:51]


simulate_mrp_data<-function(n) {
  J<-c(Stratas,States) # The first represents our "strata", the second our state
  poststrat<-as.data.frame(array(NA,c(prod(J),length(J)+1)))
  colnames(poststrat)<-c("Strata","State",'N')
  count<-0
  for(i1 in 1:J[1]) {
    for (i2 in 1:J[2]){
      count<-count+1
      poststrat[count,1:2]<-c(i1,i2)
      poststrat$N<-NA
    }
  }

}

simulate_mrp_data()
```

```{r}
summary(ProWar_Model_Posterior)
rhats<-rhat(ProWar_Model_Posterior)
print(rhats)
mcmc_rhat(rhats)
```


```{r}
detach("package:rstanarm",unload=TRUE)
```

```{r}
BayesCoefficients<-coef(ProWar_Model_Posterior)$State
view(BayesCoefficients)
names(BayesCoefficients)<-c("Intercept","MALE","HSGrad","SomeCollege","Bachelor","Graduate","A25.34","A35.44","A45.64","A65Plus")

BayesEstimates<-BayesCoefficients %>%
  mutate(STUSPS=row.names(coefficients),
         FeNoHS18_24=invlogit(Intercept),
         FeNoHS25_34=invlogit(Intercept+A25.34),
         FeNoHS35_44=invlogit(Intercept+A35.44),
         FeNoHS45_64=invlogit(Intercept+A45.64),
         FeNoHS65=invlogit(Intercept+A65Plus),
         FeHSGrad18_24=invlogit(Intercept+HSGrad),
         FeHSGrad25_34=invlogit(Intercept+HSGrad+A25.34),
         FeHSGrad35_44=invlogit(Intercept+HSGrad+A35.44),
         FeHSGrad45_64=invlogit(Intercept+HSGrad+A45.64),
         FeHSGrad65=invlogit(Intercept+HSGrad+A65Plus),
         FeSome18_24=invlogit(Intercept+SomeCollege),
         FeSome25_34=invlogit(Intercept+SomeCollege+A25.34),
         FeSome35_44=invlogit(Intercept+SomeCollege+A35.44),
         FeSome45_64=invlogit(Intercept+SomeCollege+A45.64),
         FeSome65=invlogit(Intercept+SomeCollege+A65Plus),
         FeBach18_24=invlogit(Intercept+Bachelor),
         FeBach25_34=invlogit(Intercept+Bachelor+A25.34),
         FeBach35_44=invlogit(Intercept+Bachelor+A35.44),
         FeBach45_64=invlogit(Intercept+Bachelor+A45.64),
         FeBach65=invlogit(Intercept+Bachelor+A65Plus),
         FeGrad18_24=invlogit(Intercept+Graduate),
         FeGrad25_34=invlogit(Intercept+Graduate+A25.34),
         FeGrad35_44=invlogit(Intercept+Graduate+A35.44),
         FeGrad45_64=invlogit(Intercept+Graduate+A45.64),
         FeGrad65=invlogit(Intercept+Graduate+A65Plus),
         MaNoHS18_24=invlogit(Intercept+MALE),
         MaNoHS25_34=invlogit(Intercept+MALE+A25.34),
         MaNoHS35_44=invlogit(Intercept+MALE+A35.44),
         MaNoHS45_64=invlogit(Intercept+MALE+A45.64),
         MaNoHS65=invlogit(Intercept+MALE+A65Plus),
         MaHSGrad18_24=invlogit(Intercept+MALE+HSGrad),
         MaHSGrad25_34=invlogit(Intercept+MALE+HSGrad+A25.34),
         MaHSGrad35_44=invlogit(Intercept+MALE+HSGrad+A35.44),
         MaHSGrad45_64=invlogit(Intercept+MALE+HSGrad+A45.64),
         MaHSGrad65=invlogit(Intercept+MALE+HSGrad+A65Plus),
         MaSome18_24=invlogit(Intercept+MALE+SomeCollege),
         MaSome25_34=invlogit(Intercept+MALE+SomeCollege+A25.34),
         MaSome35_44=invlogit(Intercept+MALE+SomeCollege+A35.44),
         MaSome45_64=invlogit(Intercept+MALE+SomeCollege+A45.64),
         MaSome65=invlogit(Intercept+MALE+SomeCollege+A65Plus),
         MaBach18_24=invlogit(Intercept+MALE+Bachelor),
         MaBach25_34=invlogit(Intercept+MALE+Bachelor+A25.34),
         MaBach35_44=invlogit(Intercept+MALE+Bachelor+A35.44),
         MaBach45_64=invlogit(Intercept+MALE+Bachelor+A45.64),
         MaBach65=invlogit(Intercept+MALE+Bachelor+A65Plus), 
         MaGrad18_24=invlogit(Intercept+MALE+Graduate),
         MaGrad25_34=invlogit(Intercept+MALE+Graduate+A25.34),
         MaGrad35_44=invlogit(Intercept+MALE+Graduate+A35.44),
         MaGrad45_64=invlogit(Intercept+MALE+Graduate+A45.64),
         MaGrad65=invlogit(Intercept+MALE+Graduate+A65Plus)) %>%     # We include a geometry variable in order to create a bind later
         dplyr::select(-Intercept,-MALE,-HSGrad,-SomeCollege,-Bachelor,-Graduate,-A25.34,-A35.44,-A45.64,-A65Plus)


print(BayesEstimates)

# This will result on us getting everything, as the estimated percentage for everything. 
```

```{r}
BayesEstimates<- BayesEstimates %>% arrange(STUSPS)
CellPerc2<-CellPerc2 %>% arrange(STUSPS)

BayesProbabilityPro<-BayesEstimates[,2:51]

metadataStateGIS3<-metadataStateGIS2 %>% mutate(BayesEstimatedProbability=NA) %>% dplyr::select(BayesEstimatedProbability, c(colnames(metadataStateGIS2)))

metadataStateGIS3 <-metadataStateGIS3 %>% arrange(STUSPS)

for (i in 1:51) {
  metadataStateGIS3[i,1]<-(sum(Weights[i,]*BayesProbabilityPro[i,])*100)
}

```

```{r}
metadataStateGIS3<-metadataStateGIS3 %>%
  mutate(fips=GEOID)

plot_usmap(data = metadataStateGIS3, values="BayesEstimatedProbability",color="white")+scale_fill_continuous(name="% who Believe that War is Effective",label= scales::comma)+theme(legend.position="right")
```

```{r}
library(bayesplot)
```
```{r}
BayesianCoefficientList<-names(ProWar_Model_Posterior$coefficients)

color_scheme_set("blue")

length(BayesianCoefficientList)

```


```{r}

mcmc_trace(ProWar_Model_Posterior,pars = BayesianCoefficientList[1:5])
mcmc_trace(ProWar_Model_Posterior,pars = BayesianCoefficientList[6:10])
mcmc_trace(ProWar_Model_Posterior,pars = BayesianCoefficientList[11:15])
mcmc_trace(ProWar_Model_Posterior,pars = BayesianCoefficientList[16:20])
mcmc_trace(ProWar_Model_Posterior,pars = BayesianCoefficientList[21:25])
mcmc_trace(ProWar_Model_Posterior,pars = BayesianCoefficientList[26:30])
mcmc_trace(ProWar_Model_Posterior,pars = BayesianCoefficientList[31:35])
mcmc_trace(ProWar_Model_Posterior,pars = BayesianCoefficientList[36:40])
mcmc_trace(ProWar_Model_Posterior,pars = BayesianCoefficientList[41:45])
mcmc_trace(ProWar_Model_Posterior,pars = BayesianCoefficientList[46:50])
mcmc_trace(ProWar_Model_Posterior,pars = BayesianCoefficientList[51:55])
mcmc_trace(ProWar_Model_Posterior,pars = BayesianCoefficientList[56:61])

```

```{r}
mcmc_intervals(ProWar_Model_Posterior,pars = BayesianCoefficientList[1:10])
```

```{r}
mcmc_trace(ProWar_Model_Posterior,pars="AgeBracket25-34")
```


```{r}
ratio<-neff_ratio(ProWar_Model_Posterior)

mcmc_neff(ratio,size=2)
```
It is noted by the authors that we should only be worried about a low N_eff/N is the value is below .1. This is not the case in this regard. There are, certainly a few variables that may have some mild concerns, but nothing too worrying. 
