---
title: Estimating Pro-War and Anti-War Sentiments by State Using Multilevel Regression with Poststratification
author: "Parker Kaukl"
date: 5/17/2022
output:
  pdf_document: default
  html_document:
    df_print: paged
fontsize: 11pt
indent: true

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, fig.height=3, fig.width=6)
# feel free to change fig.height or fig.width here or in specific chunk headings. 
```



```{r, include=FALSE}
library(tidyverse)
library(knitr)
library(lme4)
library(lmerTest)
library(gridExtra)
library(corrplot)
library(GGally)
library(kableExtra)
library(arm)
library(usmap)
library(dplyr)
library(tidycensus)
library(stargazer)
library(coda)
library(rstanarm)
library(bayesplot)
library(stringr)
library(ggrepel)
```


```{r}
 load("Workspace.RData") # This is data that had previously been collected from the previous files.
```
## Abstract

One of the most complex topics in american politics is military intervention. Public opinion on military intervention is historically divided into pro-war and anti-war positions. Understanding which states may be more or less likely to be pro or anti War is important for predicting which areas may have more protests, and inform policy positions for elected officials. This paper will create a model to predict opinions on war using a Frequentist and a Bayesian approach. Then, these models will be used in order to create a Multilevel Regression with Post-Stratification to estimate the public opinion within each state in the United States of America. In both the Bayesian and the Frequentist approaches, our Multilevel Regression with Post-Stratification estimates that the public opinion within each state to believe that War is effective is between 60% and 70%. These results tend to be similar to the public opinion polls on military interventions throughout the late 2010s.
\newpage


### Introduction


The decision to go to war is a complex decision that has severe consequences. A report from Brown University estimated that around 900,000 deaths occurred in the War on Terror. These fatalities  include soldiers, civilians, journalists and aid workers.In addition, the U.S.'s War on Terror has incurred a cost of $8 trillion dollars since 2001. Because of these high societal costs, it is not surprising that conflict tends to be a polarizing topic, and a topic that has attracted theories on when conflict may occur. 

One of the first theories of War is the "Just War" theory, by St. Augustine. This posited that conflict should occur if it is for a worthy cause, if conflict is likely to achieve that cause and if the conflict is sponsored by a legitimate government. "Just War" theory also states that conflict should only be used as a last resort, that conflict should not be disproportionate to the cause, and that non-combatants should be respected. Although this theory is valuable, the discourse on military conflict has been furthered by philosophers, politicians, and theologians over the past centuries. 

However, perhaps the most relevant and important influence on our perception of war has been the United State's recent history of war. A lot of theories and thoughts on war were developed in the aftermath of the Vietnam War. As noted in Richard Haas's book, Intervention, the Vietnam War was an event that informs both our policymakers and citizens on what War is like. Perhaps more importantly, the Vietnam War and the protests related to U.S. involvement introduced the importance of U.S. public opinion to whether we should engage in military conflicts. 

Caspar Weinberger, a Secretary of Defense under Ronald Reagan, introduced the Weinberger Doctrine, which stated that force should only be used if there is public or congressional support for military conflict. This was furthered by Warren Christopher, the Secretary of Defense under Bill Clinton, who said that having "a high likelihood of support" of popular and congressional support was a prerequisite for military intervention. Other Politicians have not mentioned public opinion as a prerequisite, but have mentioned that it is desirable to have support for any military intervention. 

The Effects of Public Opinion during Wartime are numerous. As noted by George Gallup, Public Opinion can often coincide with political changes. As stated in _How Important is Public Opinion in Time of War?_, "In addition to conscription, the people of this country have been ahead of their political leaders on virtually all important war-time issues" (Gallup, 441). In addition, conflict is often likely to not occur, or forces are likely to be withdrawn in the case of public disapproval. This can be seen in a lack of approval for U.S. intervention in Somalia, and later the U.S.'s lack of military intervention in Rwanda during the Rwanda Genocide. In addition, the mismanagement of military intervention threatens re-election campaigns for politicians. Because of this threat, "Politicians--Whose foremost goal is to gain or retain office- will, in an electoral context, be motivated to support changes in war policy if opinion trends among their constituents offer an incentive to do so" (Lieberfeld, 2008). Public Opinion acts as a political constraint to the use of force, in addition to providing probable policy platforms during upcoming elections. 

For policymakers, understanding public opinion is crucial to making the correct decision about when it is appropriate to use military force. In addition, for citizens, public opinion can provide a good predictor of future policy decisions. Therefore, this paper will attempt to create a Frequentist and a Bayesian model in order to estimate the public opinion on military intervention based off a series of surveys known as the *Chicago Council Survey of American Public Opinion on U.S.Foreign Policy* from 2016 and 2017. The Survey question that we will analyze focuses on the public opinion on the effectiveness of war in achieving the foreign policy goals of the United States. Using this data, we will estimate the expected political support in each U.S. state in 2016 and 2017. This will be done using a method known as Multilevel Regression with Post-stratification, using data from the American Community Survey. Then, this paper will attempt to validate these models by checking that there are no errors in this model, and observing if national surveys from 2015 to 2019 produce similar national results to the evidence that I have found. 

### Background and Significance

There have been numerous opinion polls and regressions that have been run in order to estimate pro or anti war opinion during the "post cold war" era. There are a few reasons why authors and academics tend to start their analysis of war trends in the "post cold war" era. In general, the individual's personal policy preference on war tends to be very temporal. The cold war provided a very unique circumstance, such as the policy of deterrence and the fear of a global war, that does not necessarily reflect the current circumstances of conflicts in the "post cold war" era. Because of this, our scholarship tends to focus on the "post cold war" era as a separate era to the cold war era. 

According to Gelpi and Feaver, the determination of a citizen's preference is based on that individual's demographics, and the context of the situation. Specifically, individuals tend to be in support of military intervention if they believe that they have the "Right" to attack, and they believe that military intervention will be successful to achieve their preferred policy goals. Many of these contextual results are likely to reflect incredibly temporal events that are vulnerable to political changes. For instance, individuals tend to look towards individuals such as politicians that they trust, and organizations such as NATO. If an organization like NATO, or a president that they trust endorse a military action, individuals are extremely likely to support that military interaction. This was found by both Olga Khazan(2013) and by Gelpi and Feaver(2009). 

In addition, individuals are likely to make choices depending on the Principal Policy Objective, according to Jentleson (1992). This thesis argues that individuals have different values, and that the primary objective of why is going to war is likely to influence the level of political support for intervention. For instance, according to a poll from Jentleson, individuals tend to be more in support of Foreign Policy Restraint missions, as opposed to Internal Political Change missions. Foreign Policy Restraint typically involves the use of military force in order to affect the behavior of a nation, whereas Internal Political Change Missions involve using the military to replace or restructure an existing regime. 

Finally, individuals also tend to support missions that they believe will be successful. As noted by Gelpi and Feaver (2009), public support for military intervention tends to drastically decreasing during periods of failure. For instance, In the aftermath of a failed raid in Somalia in 1993, public support for military intervention dropped by 8 percentage points. In general, individuals tend to support a war when there is evidence that there is some level of success. 

While these circumstantial predictors are important, there are additional variables that might be important in order to predict pro vs. antiwar sentiment. These variables are demographic, and tend to be less dependent on the context of the conflict in determining public opinion. For instance, our evidence of gender suggests that there is a mixed effect of whether women or men are more supportive of conflict. Gelpi and Feaver wrote *Paying the Human Costs of War*, which collects regressions that indicate that there is conflicting evidence about the effect of gender in being pro or antiwar. Men were more supportive of military intervention in Lebanon in 1983. Men also tended to be more supportive of military intervention in Somalia in 1993. In the early 2000s, a general poll reported by Gelpi and Feaver stated that there was no statistical significance in gender in determining whether an individual supports military intervention. However, evidence from polls taken during the Kosovo crisis suggests that Women were more likely to support military intervention through Air strikes in the Kosovo War. Women were also more likely to fall into the category that Gelpi and Feaver refer to as "Timid Hawks". Gelpi and Feaver use this term to classify individuals who are supportive of War in the abstract, but tend to withdraw their support as the war becomes costly, or as casualties from the conflict increase. This is also important to note, as it highlights a major theme of Gelpi and Feaver, which is that casualty tolerance is not the same thing as conflict tolerance. 


Another variable that is very important to consider is age. Anecdotally, there is evidence that suggests that age can both increase and decrease support for War. Many historians note the fervor that younger men tended to have, and their excitement for World War 1. Meanwhile, Vietnam War Era protests are remembered for the swarms of college students who protested against the U.S's involvement in Southeast Asia. However, data tends to provide a conflicted history of who tends to be more pro war. Older individuals were less likely to support a military intervention in Lebanon and in Somalia. However, older individuals were less likely to support the Iraq War (Smith and Lindsay, 2003). However, age did not appear to play any significant role in whether an individual supported intervention in the Kosovo War. In general, the role that age plays in determining pro and anti war support appears to be inconsistent. 

The role of education in determining pro and anti war stance tends to be very consistent. These estimates tend to suggest that individuals with higher levels of education may be less likely to support war. People were less likely to support a military intervention in Kosovo with higher levels of education. In addition, people with higher levels of education were less likely to support the use of force if the objective of the mission is a matter of national security. However, education did not have a significant change for whether an individual supported military intervention in Yemen or in Lebanon. In addition, according to Smith and Lindsay (2003), education plays a major role in determining support. Individuals with a postgraduate education were among the few groups who were not in favor of the Iraq War in late 2002. 

There are many different additional variables that might be important in determining which individuals will support or not support a war. For instance, people tend to support a war if that war was initiated by the party that aligns with their own personal politics. For instance, democrats tend to be more supportive of military intervention if a democratic president initiated that war, and republican voters are more likely to support wars initiated during a republican presidency. In addition, individuals who are veterans tend to be less likely to support military intervention, as found by Khazan (2013). The affect of other demographic variables, such as Race, tend to have inconsistent evidence on the direction and the significance of the effect of racial identity on pro and antiwar stance. 




### Data

The first dataset that I used was the Chicago Council Survey of American Public Opinion on U.S. Foreign Policy. This is an annual survey that asks questions related to the foreign policies in the United States, and the public opinion on these policies. For the purpose of my data, I am using the 2016 and 2017 Chicago Council Survey of American public Opinion. These two years were used because they are both publically available, and they both have a question that is coded the same. The target population of this survey was those living in the U.S. who were non-institutionalized and who are aged over 18. The survey was administered by the KnowledgePanel, which is a probability based web panel designed to be representative of the U.S. results. The administrators of this survey included various checks, such as removing those who answered the test too quick and those who failed the "quality checks". The "quality checks" consisted of questions such as "Pick option 3", which indicates whether a respondent was actually attentive during the survey. The Chicago Council Survey has 4767 observations over the 2 years. 

In order to clean this data, we took multiple steps. First, any cases where there was a missing value were discarded, in order to prevent any bias that might occur by keeping these variables in the dataset. In addition, many of the variables were manipulated in order to create new variables for the purpose of a regression. Initially, there was a variable called *Q8_14*. This variable recorded the respondents answer to the question *How effective do you think each of the following approaches are to achieving the foreign policy goals of the United States- very effective, somewhat effective, not very effective, or not effective at all: Intervening Militarily*. Using this variable, we manipulated it into a new variable called *ProWarBinary*. If this variable is equal to 1, then the respondent believes that military intervention is either very effective or somewhat effective. Meanwhile, if the respondent believes that military intervention is not very effective or not effective at all, then the variable will return with a value of 0. 

In addition, the Chicago Foreign Council data also had additional variables that reflect the demographics of the respondents. In this case, the variables includes information about the racial, political, social, economic and family history of the respondent. There are a few variables of note that will later be used in the model to build the Multilevel Regression with Post stratification. The variable *EducationBracket3* represents a subset of different levels of education. This includes a variables for those who did not get a High School Diploma, those with a High School Diploma, those with some college, those with a bachelor's degree, and those with more education than a bachelor's degree. 

Another variable of note is *AgeBracket*. This variables indicates what strata of age the respondent is in. Respondents can either be in a strata for those aged 18 to 24, 25 to 34, 35 to 44, 45 to 64, and for those who are 65 or older. These stratas were constructed to match the format of the stratas that are reported in the ACS. In addition, the Chicago Foreign Council also included information about what state a respondent was from, reported in the variable titled *State*. 

There are some checks that we may want to do in order to evaluate whether there was any response bias. In presenting the question represented in variable *Q8_14*. In the survey, this response could have been showed anywhere between first and eighth. We might suspect that the order that Military Intervention is presented will influence the response and create response bias. One method can be checking if the order to the response is likely to change the effect of whether an individual thinks military intervention is effective or not depending on when the respondent is presented with the policy choice of military intervention. 

```{r}
ChicagoForeignCouncilClean<-ChicagoForeignCouncilClean %>% mutate(
  StatementNumber=as.factor(as.numeric(ifelse(Year==2016,substring(DOV_Q8_14,2,2),
                             substring(DOV_Q8_14,2,3)))))
  #this is being done to adjust for the fact that there is a slight difference in how statement order was coded. 
```

```{r, fig.cap="Proportion of Belief in Effectiveness of War"}
ggplot(ChicagoForeignCouncilClean,aes(x=StatementNumber,fill=ProWarFactor))+geom_bar(position=position_fill())+xlab("Position that the Statement was Shown In")+ylab("Proportion of Respondents")+scale_fill_discrete(name = "Pro War Factor", labels = c("Military Intervention is not Effective","Military Intervention is Effective"))
```

Figure 1 illustrates the response of the effectiveness of war, based on the Variable *ProWarFactor*. There is not a lot of variation in the responses of the effectiveness of war depending on the position that the statement was shown in. For instance, we can see that people who were shown this statement earlier may report being more in favor of war, as opposed to those who were asked about military intervention later. However, it appears like the position that the statement was shown in does not carry a significant level of bias, and therefore we can consider that source of response bias as insignificant. 

We can also observe other relationships in our data. One particular question might be whether individuals have different levels of support based on what region they live in. Different cultural values and different regional relationships with the military may determine the different levels of support for military conflict. For instance, Karol and Miguel (2007) tested whether different regions had different levels of political support for reelecting George W. Bush based on the number of casualties in Iraq, based on the speculation that different geographic regions had different relationships with the War. Therefore, observing the prowar and antiwar levels of support within each U.S. region may be important to determining if there is a different level of support depending on geographic region. 

```{r, fig.cap="Belief in the Effectiveness of War by Region of Residence",fig.height=4}
ggplot(ChicagoForeignCouncilClean,aes(x=Region9,fill=ProWarFactor))+geom_bar(position=position_fill())+xlab("Region the Respondent Lives In")+ylab("Proportion of Respondents")+scale_fill_discrete(name = "Pro War Factor", labels = c("Military Intervention is not Effective","Military Intervention is Effective"))+theme(axis.text.x=element_text(angle=90))
```

On Figure 2, we are able to see that there does appear to be some slight differences between different regions in determining the pro and anti war support for the effectiveness of war. The New England region has less support for conflict than the other regions. However, the West-South Central region and the East-South Central Region both tend to be more supportive of conflict than other regions. However, the significance of these responses is not clear based on Figure 2. 

In addition, we are able to observe whether there are differences in pro war and anti war sentiment based on education. This is observed in Figure 3, which indicates that there is some correlation between education level and belief in the effectiveness of war. For people who did not receive an high school diploma, roughly 75% of respondents believed that military intervention is an effective method to achieve the U.S's foreign policy goals. However, for those with a postgraduate degree, about 50% of respondents believed that military intervention is likely to achieve the U.S's foreign policy goals. In addition, Figure 4 illustrates that there is some potential relationship between age and support for military intervention. Those who were between ages 18-24 and 45-64 are more likely support intervention, relative to other age brackets. However, this relationship does not appear to be as strong as other relationships. 

```{r, fig.cap="Belief in the Effectiveness of War by Level of Education",fig.height=4}

ggplot(ChicagoForeignCouncilClean,aes(x=EducationBracket3,fill=ProWarFactor))+geom_bar(position=position_fill())+theme(axis.text.x=element_text(angle=90))+xlab("Level of Education")+ylab("Proportion of Respondents")+scale_fill_discrete(name = "Pro War Factor", labels = c("Military Intervention is not Effective","Military Intervention is Effective"))
```

```{r, fig.cap="Belief in the Effectiveness of War by Age"}
ggplot(ChicagoForeignCouncilClean,aes(x=AgeBracket,fill=ProWarFactor))+geom_bar(position=position_fill())+xlab("Level of Education")+ylab("Proportion of Respondents")+scale_fill_discrete(name = "Pro War Factor", labels = c("Military Intervention is not Effective","Military Intervention is Effective"))
```

Another dataset that was used in this analysis is the American Community Survey. The American Community Survey, or ACS, is a survey that has information on individuals and households throughout the country. In particular, this data focuses on the demographics, occupations, education and other background info of any respondents. The data that was used in this paper was the summary statistic named *B15001*, from the 5-Year ACS between 2015 and 2019. This data includes the raw count of number of respondents who were in a certain strata defined by gender, education level and age bracket. These stratas are pairwise disjoint, as it would require individuals to belong to multiple brackets. Then, I created a new variable, titled *TVP*, standing for Total Voting Population. This was the sum of all of the stratas. I then divided each strata by the variable *TVP*, in order to get an estimation of the proportion of each strata within each state.

The ACS does have a few problems with it that make it a suboptimal resource in order to estimate proportions. The ACS does not ask questions about values such as what political party an individual identifies with, or what foreign policy goals the U.S. should have. These questions may be important in relation to pro and anti war sentiment. These problems will be of particular concern during the implementation of a Multilevel Regression with Post Stratification model. 


### Methods 

This paper will focus on using a Multilevel Regression with Poststratification, or MRP. A Multilevel Regression with Post Stratification is a method to estimate public opinion for areas that are smaller than the national level, such as individual states. It is highly unlikely that there will be multiple state surveys that will all ask the same questions using similar wording and surveying methods. Because of this, statisticians have developed strategies to use national level opinion polls to estimate public opinion for smaller geographic areas. One method is disaggregation, which is where national surveys are pooled in order to calculate public opinion. However, MRP has become an alternative method to disaggregation. MRP has been shown to outperform disaggregation with small and medium sized samples, and can estimate state public opinion with a single large national poll of roughly 1,400 respondents(Gelman, 2018). MRP is better suited for estimating public opinion issues that are swayed heavily by circumstances. In addition, MRP is useful for estimating the responses in smaller states that do not have a large number of respondents who reside in those states. Because of these advantages, building an MRP model is preferable to using a model of disaggregation to estimate the beliefs on the effectiveness of war in each U.S. State. Multilevel regression with Poststratification has been used frequently by statisticians to estimate public opinion by geographic area. For instance, Bohr(2014) used MRP to estimate the probability of an individual in each U.S. county believing in Climate Change, and understanding their preferences for environmental policy. In addition, Wang (2014) used MRP in order to estimate the voters preferences for the U.S. election in 2012 by using surveys submitted through the online platform Xbox Live, which estimated the share of votes to Barack Obama with a margin of error of .6 percentage points. 

There are a few steps needed in order to create an MRP. First, data needs to be collected that focuses on public opinion data, and different potential predictors. Next, there would need to be census data collected in order to estimate the proportion of different stratas in each state. We would also need to estimate the probability of believing U.S. intervention is effective within each strata based on our public opinion data, using a logistic regression from the Chicago Council Surveys. Then, using our estimates of the probability of any person within a strata being pro war, we poststratify these models using the proportional size of the strata relative to the rest of the state. 

One important detail in an MRP is that we are required to have the design of the logistic regression and the design of the ACS must be cohesive in order to effectively implement an MRP. An MRP works because it is accurately able to assign each predicted response based on our regression to our weights for poststratification. Therefore, there would be significant problems in using a Multilevel Regression with Post Stratification if the multilevel regression includes terms that are not included in poststratify weights. This would result in us having predicted response probabilities without any understanding of what the approximate weights of these responses will be. 

Therefore, in building our logistical regression, we will attempt to reduce the AIC and we will only build a model where we can also estimate the weights of these different responses based on the ACS data. In addition, the model that we analyze will also focus on the most important aspects that may have been identified in our data section. For instance, one important variable to use in our regressions would be education. Education level is a variable that shows a clear relationship to pro vs. antiwar sentiment. There are roughly 1000 different distinct counts that exist in the ACS data. However, only about 30 different types of counts include educational attainment as a key variable. In addition, very few of these variables account for the full voting aged population. 

The best model that we could find that includes variables that could be weighted in the census was a model which used educational attainment, gender, and age brackets. However, the state was also used as a random effect. This model produced the smallest AIC of any adequate model that was built in this experiment, at a value of 6130.953[1]. We can therefore write the estimated model as a two part section. The first part represents our Post-stratification, where we multiply the probability of support of pro war by each strata within the state by the probability of any given person in that state being within that strata. We then sum the product of all these probabilities in order to estimate the probability of support within each state. The second line through fourth lines represents our multilevel model, which includes a random effect for the State, in order to account for variations in public opinion within each state that are not accounted for by our model. Finally, our estimation of the probability of being within each strata is defined by calculating the percent of people within each state $j$, who were in Strata $i$ as a percent of the total voting population. 


\begin{flalign}
& P(\theta_{j}=1|\text{State=j})=\sum_{i=1}^{50}P(\theta_{ij}=1|\text{Strata}=i)*P(\text{Strata}=i|\text{State}=J) &\\
& P(\theta_{ij}=1|\text{Strata}_{j}=i)=\text{logit}^{-1}(\alpha+\beta_{1}*\text{Male}_{i}+\beta_{2}*\text{High School Degree}_{i} &\\
& +\beta_{3}*\text{Some College}_{i}+\beta_{4}*\text{Bachelor Degree}_{i}+\beta_{5}*\text{Graduate Degree}_{i}+\beta_{6}*\text{25 to 34}_{i} &\\
& +\beta_{7}*\text{35 to 44}_{i}+\beta_{8}*\times{45 to 64}_{i}+\beta_9*\text{65+}_{i}+u_{j}+\epsilon{ij}) &\\
& u_{j}\sim \mathcal{N}(0,\,\sigma_{u}^{2}) &\\
& \epsilon{ij}\sim \mathcal{N}(0,\,\sigma_{\epsilon}^{2}) &\\
& P(\text{Strata}=i|\text{State}=J)=\frac{\text{Population in Strata I in State j}}{\text{Total Voting Population in State J}} &
\end{flalign}

$\theta$ represents whether an individual believes that war is effective or ineffective at achieving the U.S.'s policy goals. $\alpha$ represents the intercept, which would calculate the probability a Women who is between the ages of 18 to 24 with less than a high school education believes that war is effective. Each of the subsequent $\beta$'s then represent the effect of individual effects, such as identifying as a man, or having a Graduate Education, on pro vs. antiwar sentiment. The value $u_j$ is the random effect that being within a certain state has on their beliefs of war, while $\epsilon_{ij}$ is the random error term. 

By construction, our stratas will be pairwise disjoint and they will cover the voting aged population. The stratas are broken up into categories based on age, sex, and educational obtainment. In addition, it is not possible for an individual in the voting age population to not fit into any of the stratas, or for them to fit into multiple stratas. This is important to ensuring that our MRP model will be successful in estimating the probability of an individual's beliefs on war within a certain state. 

This paper will also build a logistic regression under a Bayesian framework. This would require us to set our priors. These priors would be based on the background research, mostly from the regressions that are in Gelpi and Feaver (2009). Using logistic regressions on public opinion on conflict, we should be able to have an estimate of the effects of gender, education, and age on an individual's beliefs on war. 

The expected prior for the effect of beliefs on war for gender is rather complex. For instance, traditional studies that focused on War, particularly in the 1980s and 1990s, tend to suggest that men tend to be more supportive of conflicts. However, this is contrasted with some contemporary data. For instance, Women tended to be more likely to be classified as "Timid Hawks". In addition, women tended to have higher levels of support for military intervention is Kosovo, and for Humanitarian Missions in Yemen. There are two very important distinctions to be made in our previous data, the age of the data that we are observing, and how similar these surveys are to the Chicago Council survey question that we analyzed. For instance, more recent data tends to suggest women may be more likely to believe in conflict than men. In addition, when asked about military intervention before it happened, women tended to be more likely to support intervention, as seen in supporting intervention in Kosovo and Yemen. This is similar to the structure of the Chicago Foreign Council question, as it asks for the respondents level of support before any military intervention has occurred. Because of this bias, there is some evidence that Men may be slightly less likely to believe that war is effective in the abstract. Because of this, it might make sense to assign that the prior for gender is a vague prior with a slight preference to show that women may prefer military conflict. Because of this, a prior of $Male\sim N(-.1,1)$ may be appropriate. The standard deviation suggests that we believe it is plausible that the effect could be far greater. 

Another important prior to set is the expectations for the priors by age bracket. Most of these surveys use age as a continuous variable, instead of establishing different age brackets. However, these linear relationships tend to suggest that the effect of age on support for war tends to be roughly close to 0. In many of these regressions, the effect of age was also not statistically significant. Therefore, there may be some value in establishing a vague prior, since there is not strong evidence establishing a trend. Therefore, we might decide to use a prior, where for each age bracket we assume that the coefficient has a normal prior, with a mean of zero and a standard deviation of 1. 

Finally, a prior would need to be set for the effect of education on beliefs of war. In older studies, such as examining support for conflicts in Lebanon and Somalia, there was not a very strong relationship between the level of education and an individual's preference for military conflict. However, In Kosovo, higher levels of education lead to an individual to be less likely to support military intervention. In addition, individuals were more likely be classified as "timid hawks" if they had more education. Because of these relationships, we might expect that the prior is that higher levels of education result in a lower likelihood of supporting war. Arbitrarily, some priors can therefore be set. For instance, we may establish that every subsequent level of education will affect education by -.2. Therefore, we might establish that each of our levels of education has an independent prior, as established below. 

\begin{flalign}
&\text{High School Graduate}\sim N(-.2,1) &\\
& \text{Some College} \sim N(-.4,1) &\\
& \text{Bacehlor Degree} \sim N(-.6,1) &\\
& \text{Graduate Degree} \sim N(-.8,1) &
\end{flalign}

### Frequentist Results  

On Table 1, we are able to see the effects of each standard effect in our model, as outlined previously on our equation through lines 2 to 4. We are able to see that the estimated intercept on this equation is 1.1191. This indicates that we expect that the average Women, aged between 18-24 and that did not obtain a high school diploma is 75.38% likely to believe that military intervention is effective, before accounting for the random effect of the state.  According to our data from the Chicago Council, all else held equal, men are 23.5% less likely to believe that military intervention is an effective method of achieving the U.S.'s policy goals. These results are statistically significant. 

The effects of education are also very evident, based on our model. A respondent who had graduate from high school was 21.56% less likely to believe that military intervention is effective in achieving the U.S.'s goals, when compared to individuals who did not achieve a high school education. However, these results were not statistically significant at the 5% level. Meanwhile, respondents who attended some college were likely be 38.07% less likely to believe in military intervention as effective when compared to those who did not achieve a high school education. Respondents who got a bachelor's degree were 46.31% less likely to believe that military intervention was effective compared to those who did not get a high school diploma. Finally, respondents who had a postgraduate education were 64.67% less likely to believe that war is effective compared to those who did not get a high school diploma. All of these results were statistically significant at the 5% level. 

```{r, fig.cap="Estimates of Fixed Effects",fig.width=6}
M25Table<-summary(M25)$coefficient
rownames(M25Table)<-c("Intercept","Male","High School Graduate","Some College","Bachelor's Degree","Graduate Degree","Age 25 to 34","Age 35 to 44","Age 45 to 64","Age 65 or older")
kable(M25Table,digits = 4,format="pipe",caption = "Estimates of Fixed Effects")
```
The final set of fixed effects are related to the age of the respondent. People who are in the age range from 25 to 34 are 2.19% less likely to believe that military conflict is an effective strategy to achieve the U.S's foreign policy goals. However, these results are not statistically significant. Respondents who are aged 35 to 44 were 14.83% more likely to believe that military intervention is effective, but this result was not statistically significant. People aged 45 to 64 were 26.07% more likely to believe that military intervention, compared to people who were aged 18 to 24. These results were only statistically significant at the 10% level. 

Using our estimates, we are able to guess what the potential public opinion within each state may be. Therefore, this data can be displayed on Figure 5. Some states and regions tend to have a lower opinion of war than other states, as illustrated by the Map. However, in general, most states tend to have a level estimated 60 to 70% of voting aged adults within that state who believe that War is effective at achieving the U.S's goals. States such as California, Massachusetts, and Minnesota all have roughly 62% of their citizens who believe that military intervention is an effective strategy to achieve the U.S's goals. Meanwhile, in Texas roughly 68% of citizens believe that military intervention is an effective strategy to achieve the U.S's foreign policy goals. Other states, such as Arkansas, North Carolina, and Indiana, also have comparatively high levels of public belief that military intervention is effective. 

```{r, fig.cap="U.S. Map of Public Opinion on the Effectiveness of War under a Frequentist Model"}
plot_usmap(data = metadataStateGIS2, values="EstimatedProbability",color="white")+scale_fill_continuous(name="% who Believe that War is Effective",label= scales::comma)+theme(legend.position="right")
```

```{r, fig.cap="Differences in estimates of Public Opinion within Each State, from an MRP and a Simple Disaggregation Model",fig.height=4}
ggplot(data=df2,aes(x=Number.Sampled,y=(EstimatedProbability-PercentSupportSampled),label=State))+geom_point()+geom_text_repel(size=3)+theme_minimal()+xlab("Number of Respondents from Each State")+ylab("Squared Difference of Estimates of Beliefs on War")+geom_hline(yintercept = 0,color="red")
```

Another interesting detail will be observing the comparison of using MRP and using disaggregation in order to estimate the probability that an individual is supportive of war. Disaggregation is a blunt method, where we first break a national survey into each subsequent, smaller region, and then use the raw percent of responses from that subset of the survey to estimate public opinion without any model. The difference between the MRP model and a simple disaggregation model is illustrated on Figure 6. On this graph, points above the red line indicate that the MRP estimate is greater than the estimate provided by observing at the percent who believed war was effective in the poll within each state. Likewise, points below the red line indicate that the MRP based estimate is lower than the estimate provided by observing the percent who believed war was effective within each state. Within some states, such as Hawaii, Vermont, Kansas, and North Dakota, the estimates are substantially different between these two methods. 

### Bayesian Results

Table 2 illustrates the results of running a Bayesian model, using the priors from the methods section. Before accounting for the random effect of what state the respondent lives in, a 18 to 24 year old women who does not have a high school diploma has a 75.46% probability of believing the war is an effective strategy to achieve foreign goals. Men are 23.44% less likely to support war, all else held equal. Meanwhile, high school graduates are 21.39% less likely to believe that military intervention is effective. Respondents who attended some college, obtained a bachelors degree, and attended beyond a bachelors degree were 37.97%, 46.17% and 64.52% less likely to believe that war was effective respectively, all else held equal.

The effects of age are also illustrated on Table 2. Respondents who are aged 25 to 34 were 2.76% less likely to believe that war was effective when compared to those who were aged 18 to 24. Respondents aged 35 to 44 were on average 14.02% more likely to believe that war was effective all else held equal. Respondents who were aged 45 to 64 were 25.23% more likely to believe that war was effective, while respondents who were aged 65 or older were .93% more likely to believe that war is effective. 

The results from the Bayesian analysis tend to be rather similar to the results from our frequentist model. This may be due to the fact that the priors that were used were vague. In a logistic regression a standard deviation of 1, as used in our prior, then the majority of the information on this regression will be similar to our data model if we used a simple frequentist model.

```{r}
M25TableBayes<-summary(ProWar_Model_Posterior)[1:10,c(1,3,4,5,6,7,8)]
rownames(M25TableBayes)<-c("Intercept","Male","High School Graduate","Some College","Bachelor's Degree","Graduate Degree","Age 25 to 34","Age 35 to 44","Age 45 to 64","Age 65 or older")
colnames(M25TableBayes)<-c("Mean","SD","10% Quantile","Median","90% Quantile","n_eff","Rhat")
kable(M25TableBayes,digits = 4,format="pipe",caption = "Estimates of Fixed Effects")
```

Using these results from the Bayesian Analysis, we can then undergo the same MRP process to estimate the public opinion within each state by estimating the expected value within each strata. The results of this analysis are shown in figure 7. The results of these estimates are similar to the estimates for each state generated under the frequentist model. States such as Texas, North Dakota, Arkansas and Mississippi all have larger percentages of their voting aged populations who believe that war is effective. In each of these states, we estimate that between 67% to 68% of their population believe that war is effective. However, states such as Massachussets, California, and Minnesota all have estimates that between 62% to 63% of their population believe that militaary intervention is effective. 

```{r, fig.cap="U.S. Map of Public Opinion on the Effectiveness of War under a Bayesian Model"}
plot_usmap(data = metadataStateGIS3, values="BayesEstimatedProbability",color="white")+scale_fill_continuous(name="% who Believe that War is Effective",label= scales::comma)+theme(legend.position="right")
```

In order to ensure that our model has blended well, we need to observe the R-Hat Convergence values. This value, also known as the Gelman-Rubin Convergence Diagnostic, evaluates the level of between chain convergence and within chain convergence of the estimates for each predictor. If this value is above 1.05, then it is expected that the models are not converging well, which suggests that there are significant problems. On Figure 8, the R-Hat score for each predictors is shown. Here, we are able to see that the R-Hat suggests that every predictor has converged well in this Bayesian model. 

```{r, fig.cap="R-Hat Measures for each Effect to Estimate Between- and Within-Chain Covergence"}
plot(mcmc_rhat(rhats))
```

Another important detail to analyze is the credible intervals of the Bayesian predictors. The credible intervals are displayed by observing Figure 9. This figure displays the credible intervals. By observing these credible intervals, we can note whether we expect the effects of each predictor to have a statistically significant effect. For instance, we can see that gender and education related variables tend to be statistically significant at the 5% level. The exception of the statistical significance of education related effects is the difference between those who did not complete high school, and those who completed high school. However, age based predictors are not statistically significant, based on Figure 9. 

```{r,fig.cap="The 95% Credible Intervals of Estimates for the Coefficients in the Bayesian Model",fig.height=4}
#posterior_interval(ProWar_Model_Posterior,prob=.95,type="central",pars = BayesianCoefficientList[1:10])

mcmc_areas(ProWar_Model_Posterior,pars = BayesianCoefficientList[1:10],prob_outer = .95)+scale_y_discrete(labels = c("(Intercept)"="Intercept",
                                    "MALEMALE"="Male",
                                    "EducationBracket33.Some College"="Some College","EducationBracket34.Bachelor's Degree"="Bachelor's Degree","EducationBracket35.Graduate Degree"="Graduate Degree","AgeBracket25-34"="Age 25 to 34","AgeBracket35-44"="Age 35 to 44","AgeBracket45-64"="Age 45 to 64","AgeBracket65+"="Age 65 and Over", "EducationBracket32. High School Graduate"="High School Graduate"))
```

### Discussion and Conclusions 

In both our Frequentist and Bayesian approach to estimate state level public opinion, we found that most states have between 60% and 70%. State Level opinion polls on military intervention beliefs are scarce, as most polls do not focus on state level responses. In addition, most polls do not have questions that align well with the Chicago Council Question "*How effective do you think each of the following approaches are to achieving the foreign policy goals of the United States- very effective, somewhat effective, not very effective, or not effective at all: Intervening Militarily*". Because of these problems, it may be hard to compare individual estimates of each state in our MRP model with other estimates. However, we could observe contemporary polls to observe what percent of people are in support of military intervention. In 2016 and 2017, during the period of polling, the primary concern of military intervention was the focus on military intervention in Syria against the Islamic State. 

Based on the estimates of our Bayesian and Frequentist model, weighted by the total voting population of each state, the estimated percent of national voting aged adults who believe that military intervention is effective is expected to be roughly 65%. We can then compare these results to contemporary, national surveys from a similar time period. For instance, according to Pew Research, 63% of adults supported Military Action against Islamic Militants in Iraq and Syria in 2015. In 2017, there is more evidence that individuals were in support of military intervention in Syria. According to the Morning Consult, in 2017, nearly 57% of Americans supported airstrikes in Syria, and cyberattacks, while 58% supported establishing a no-fly zone. Finally, the Airstrikes in retaliation to a chemical attack were supported by 66% of voters. Finally, 58% of voters supported the airstrikes in 2018, while 19% of those who were polled had no opinion on the airstrikes. Finally, in 2019, surveys suggested that 60% of Voters were in favor of keeping U.S. troops in Syria. Data taken on public opinion for military intervention in Syria is rather similar to the national estimates estimated by our MRP methods. 

```{r}
X1<-metadataStateGIS3$EstimatedProbability
X2<-metadataStateGIS3$BayesEstimatedProbability
X3<-metadataStateGIS3$TVP
X4<-sum(metadataStateGIS3$TVP)


USAF<-(sum(X1%*%X3))/X4
USAB<-(sum(X2%*%X3))/X4

```

Beyond the validity of our studies, there is addition things that must be noted, including the difficulties of this method, and the shortcomings of this paper. Some of the problems that we encounter include the requirement for our data on the survey, and the data on the population of each strata, must be constructed similarly. Because of this, we are limited in the variables that we might chose for the model that we may choose to build. For instance, we were not able to analyze the impact of Political Party, because these are not variables that are collected by the census. In addition, some variables are not packaged together. For instance, there was no variable that created stratas in the ACS from different variables such as Racial Identity, Veterans Status, Education Level, and Age. Therefore, in building our model, we were restricted by the ACS data. One potential solution, and opportunity for future research, is to use another form of Census, such as the Public Use Microdata, to create stratas outside of the prebuilt stratas included in the ACS. Because of time and computing restraints, I was not able to use the PUMS in order to create adequate stratas, however, future researchers may look to use the Public Use Microdata to create more adequete stratas. 

Another set of limitations from this data is the limitations presented by the question of interest. The question "*How effective do you think each of the following approaches are to achieving the foreign policy goals of the United States- very effective, somewhat effective, not very effective, or not effective at all: Intervening Militarily*" has three significant problems caused by vagueness. The first source of vagueness is term "Intervening Militarily". As noted in both Haas (1994) and Gelpi et al (2009), there are many different methods of Intervening Militarily. For instance, militaries may have troops stationed overseas, such as in military stations. However, military intervention may also look like using U.S. troops to train foreign soldiers, establishing no-fly zones, using Drones for airstrikes, or a ground invasion. All of these different military actions are likely to inspire different levels of public support. 

In addition, another source of vagueness is "the foreign policy goals of the U.S.". In the Chicago Survey, the surveyors list 16 different possible foreign policy goals the U.S. might have, including Combating International Terrorism, Protecting U.S. Jobs, Combating World Hunger, and Defending our Allies Security. It is very reasonable that, whatever foreign policy goal is specified may change the response of public opinion on the effectiveness of military intervention to achieve these goals. For instance, respondents may believe that military intervention is appropriate to Combat International Terrorism, but not to Defend our Allies Security. Without the specific foreign policy goal specified, the question must be interpretted as whether military intervention is in general a good method to achieve these goals. 

Finally, one last source of vagueness is the fact that this question does not specifically indicate the circumstances of military intervention. It is entirely conceivable, as noted by Gelpi et al. (2009) and Jentleson (1992) that individuals will give or revoke public support based on circumstantial variables. For instance, individuals might be supportive of military intervention based on what the percieved threat of non-intervention is, and what the likelihood of military success are.

Because of the vagueness of the question that we are estimating, the interpretations that we are able to make off the results of this paper are limited. We are not able to conclude specificity about public support in specific the case of specific military intervention methods, specific policy goals, or specific circumstances of the conflict. Therefore, the results of this paper can best be seen as an abstract concept of general support and belief in military intervention as an effective policy choice. 

In this paper, we used data from the Chicago Council Survey of American Public Opinion on U.S. Foreign Policy and the American Community Survey in order to estimate public support for U.S. military intervention among voting aged U.S. residents. The method used is known as a Multilevel Regression with Post stratification, which uses larger national polls to estimate the percent of support within each U.S. state. In general, we found in most states that 60% to 70% of voting aged residents believed that military intervention is effective at achieving the U.S's foreign policy goals. These results were then further supported by contemporary polls that suggest that U.S. support for intervention tended to be around 60% from 2015 to 2019. 



\newpage 

### References

Alexander, R. (2022). Telling Stories with Data. https://tellingstorieswithdata.com/

American National Election Studies. 2021. ANES 2020 Time Series
Study Preliminary Release: Combined Pre-Election and Post-Election
Data [dataset and documentation]. March 24, 2021 version.
www.electionstudies.org

British Broadcasting Corporation. (2014, November 11). The teenage soldiers of World War One. BBC News. Retrieved May 20, 2022, from https://www.bbc.com/news/magazine-29934965 

Brown University. (2021, September 1). Costs of the 20-Year War on terror: $8 trillion and 900,000 deaths. Brown University. Retrieved May 17, 2022, from https://www.brown.edu/news/2021-09-01/costsofwar 

Bohr, J. (2014). Public Views on the Dangers and Importance of Climate Change: Predicting Climate Change Beliefs in the United States through income moderated by party identification. Climate Change, 126, 217227.

Gallup, G. (1942). How Important is Public Opinion in Time of War. Proceedings of the American Philosophical Society, 85(5), 440444.

Gelman, A., & Little, T. (1997). Poststratication Into Many Categories Using Hierarchical Logistic Regression. Survey Methodology. http://www.stat.columbia.edu/~gelman/research/published/poststrat3.pdf

Gelman, A., Carlin, J. B., Stern, H. S., Dunson, D. B., Vehtari, A., and Rubin, D. B. (2013). Bayesian Data Analysis. Chapman & Hall/CRC Press, London, third edition. (Ch. 6)

Gelman, A., Lax, J., Phillips, J., Gabry, J., & Trangucci, R. (2018). Using Multilevel Regression and Poststratification to Estimate Dynamic Public Opinion. Columbia. http://www.stat.columbia.edu/~gelman/research/unpublished/MRT(1).pdf

Gelpi, C., Feaver, P., & Reifler, J. (2009). Paying the Human Costs of War. Princeton University Press.

Haas, R. (1994). Intervention: The Use of American Military Force in the Post-Cold War World. Carnegie Endowment for International Peace.

Jentleson, B. W. (1992). The Pretty Prudent Public: Post Post-Vietnam American Opinion on the Use of Military Force. International Studies Quarterly, 36(1), 4973. https://doi.org/10.2307/2600916

Johnson, A., Ott, M., & Dogucu, M. (2021). Bayes Rules! An Introduction to Applied Bayesian Modeling. Chapman and Hall.

Karol, D., & Miguel, E. (2007). The Electoral Cost of War: Iraq Casualties and the 2004 Presidential Election. The Journal of Politics, 69(3), 633648.

Kastellec, J., Lax, J., & Phillips, J. (2019). Estimating State Public Opinion With Multi-Level Regression and Poststratification using R. Princeton.

Katkov, M., Taylor, J., &amp; Bowman, T. (2017, April 6). Trump orders Syria airstrikes after 'Assad choked out the lives' of civilians. NPR. Retrieved May 30, 2022, from https://www.npr.org/2017/04/06/522948481/u-s-launches-airstrikes-against-syria-after-chemical-attack 

Khazan, O. (2013, September 4). What are the big factors determining whether Americans support war? The Atlantic. Retrieved March 29, 2022, from https://www.theatlantic.com/politics/archive/2013/09/what-are-the-big-factors-determining-whether-americans-support-war/279290/-sets-box-office-record 


Lieberfeld, D. (2008). What Makes An Effective Antiwar Movement? Theme-Issue Introduction. International Journal of Peace Studies, 13(1), 114. http://www.jstor.org/stable/41852966

Pew Research Center. (2015, July 22). A year later, U.S. campaign against Isis Garners Support, Raises Concerns. Pew Research Center - U.S. Politics & Policy. Retrieved May 30, 2022, from https://www.pewresearch.org/politics/2015/07/22/a-year-later-u-s-campaign-against-isis-garners-support-raises-concerns/ 

Sheffield, M. (2019, January 17). Poll: Most Americans want US troops in Syria. The Hill. Retrieved May 30, 2022, from https://thehill.com/hilltv/what-americas-thinking/425803-poll-most-americans-still-want-a-us-military-presence-in-syria/ 


Smeltz, Dina, Friedhoff, Karl, Kafura, Craig J., Holyk, Gregory, and Busby, Joshua W. 2016 Chicago Council Survey of American Public Opinion on U.S. Foreign Policy. Ann Arbor, MI: Inter-university Consortium for Political and Social Research [distributor], 2018-04-13. https://doi.org/10.3886/ICPSR36806.v1

Shepard, S. (2018, April 18). Majority supports Syrian airstrikes. Politico. Retrieved May 30, 2022, from https://www.politico.com/story/2018/04/18/syria-airstrikes-trump-poll-530293 

Smeltz, Dina, Daalder, Ivo, Friedhoff, Karl, and Kafura, Craig. 2017 Chicago Council Survey of American Public Opinion on U.S. Foreign Policy. Inter-university Consortium for Political and Social Research [distributor], 2021-06-21. https://doi.org/10.3886/ICPSR37970.v1

Smith, C., & Lindsay, J. M. (2003, June 1). Rally 'Round the flag: Opinion in the United States before and after the Iraq War. Brookings. Retrieved March 29, 2022, from https://www.brookings.edu/articles/rally-round-the-flag-opinion-in-the-united-states-before-and-after-the-iraq-war/ 

Wang,W., et al., Forecasting elections with non-representative polls. International Journal of Forecasting (2014), http://dx.doi.org/1-.1016/j.ijforecast.2014.06.001

Yokley, E. (2017, April 12). Americans Trust Trump the Most to End Syrian Conflict. Morning Consult. Retrieved May 30, 2022, from https://morningconsult.com/2017/04/12/americans-trust-trump-end-syrian-conflict/ 

\newpage

## Appendix

[1] There were other models that did produce AIC. However, these would not have allowed us to get a comprehensive set of weights from the ACS. For instance, some of these models would have produced estimations that we would not have any adequate weights to use in order to poststratify, according to the ACS summary statistics. Another case could be seen by the Model titled "M25b". This model included the effect of ethnicity. However, it would have not allowed us to provide weights for any individual who was between the ages of 18 and 25. This would be a large chunk of the voting population that the model would not have adequate weights for, which would be a problem. 


For information on the coding of this project, as well as the data files that were used in this project, please go to 
